---
title: "RandomSample"
output: github_document
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(source(file = "requiredfunctions.R"))
```

## Distribución Condicional de X_1 dado X_2.

Se establecen los valores de hiperparámetros phi=(a1,b1,c1,d1) y se construye la gráfica de la distribución condicional de X_1 dado X_2.

```{r, echo=TRUE, warning=FALSE}
a1=2.2; b1=2.2; c1=2.2; d1=2.2
Graph_Fc_X1(v1 = 0.05,"v=0.05",v2 = 0.10,"v=0.10",v3 = 0.20,"v=0.20",ae = a1,be = b1,ce = c1,de = d1)
```

### Monitoreo de convergencia método de simulación

Function to monitor the acceptance rate and effective size for different values of variance (v_values) and precision (prop_prec) provided

```{r warning=FALSE, echo=TRUE, results='hide'}
Mon_Measure(N=10^4, prop_prec_values=seq(1, 20, by = 1), a=a1, b=b1, c=c1, d=d1, v_values=seq(0.01, 0.24, length.out = 10),thin = 5,burnin = 500)
```

Function to monitor the R-Hat for different values of variance (s_values) and precision (prop_prec) provided

```{r , echo=TRUE,warning=FALSE,results='hide'}
Mon_R_Hat(N=10^4, prop_prec_values=seq(1, 20, by = 1), a=a1, b=b1, c=c1, d=d1, v_values=seq(0.01, 0.24, length.out = 10),thin = 5,burnin = 500)
```

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
