---
title: "RandomSample"
output: github_document
---

```{r setup, include=FALSE,echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(source(file = "requiredfunctions.R"))
a1=2.2; b1=2.2; c1=2.2; d1=2.2
```

# Introduction

This document presents a simulation framework for generating random samples from a newly proposed bivariate probability distribution, characterized by the parameter vector $\phi = (a, b, c, d)$ and the following joint probability density function:

$$
f_{\phi}(y_1,y_2)= \dfrac{1}{beta(a,b)beta(c,d)}\ y_1^{a-1}y_2^{b-1}(y_1+y_2)^{d-(a+b)} (y_1+y_2+1)^{-c-d},\hspace{1cm}y_1,y_2\in\mathbb{R}^+,
$$

where $\mathrm{beta}(\cdot, \cdot)$ denotes the Beta function. Additionally, the joint moment of order $l = l_1 + l_2$ for this distribution is given by:

$$
E_{\phi}[Y_1^{l_1} Y_2^{l_2}] \propto beta(c-l,l+d)\times beta(l_1+a,l_2+b)
$$

provided that $c > 2$, ensuring the existence of the moment.

The simulation approach integrates two key Markov Chain Monte Carlo (MCMC) techniques. First, the **Metropolis-Hastings algorithm with an adaptive random walk** is employed to generate samples from the full conditional distribution of $X_1$ given $X_2$. Second, **Gibbs Sampling** is applied to produce samples from the joint distribution of the vector $(X_1, X_2)$. Finally, these samples are transformed into realizations of the target random vector $(Y_1, Y_2)$ through the following bijective transformation:

$$
(Y_1,Y_2)=\left(X_1\left(\dfrac{X_1(1-X_1)}{X_2}-1\right),(1-X_1)\left(\dfrac{X_1(1-X_1)}{X_2}-1\right)\right).
$$

This method ensures flexible and efficient sampling from the proposed bivariate distribution, enabling further analysis and characterization of its properties.

# Generating Samples of $X_1$ Given $X_2$

## Conditional Distribution of $X_1$ Given $X_2$

The non-normalized conditional density function of $X_1$ given $X_2 = v$ is expressed as:

$$
f_{\phi}(x_1|x_2)\propto x_1^{a-c-d}(x_1(1-x_1)-x_2)^{d-1}(1-x_1)^{b-c-d}
$$

where $\phi = (a, b, c, d)$ is the parameter vector of the distribution. To illustrate the behavior of this conditional density, we set the hyperparameters to $\phi = (a1, b1, c1, d1) = (2.2, 2.2, 2.2, 2.2)$ and plot the corresponding density curves for three different values of the conditioning variable $X_2$.

```{r, echo=TRUE, warning=FALSE,fig.width=7, fig.height=4}
a1=2.2; b1=2.2; c1=2.2; d1=2.2
Graph_Fc_X1(v1 = 0.05,"v=0.05",v2 = 0.10,"v=0.10",v3 = 0.20,"v=0.20",ae = a1,be = b1,ce = c1,de = d1)
```

It is observed that the conditional density is symmetric for the configuration of $\phi$ values and that it decreases for $X_2$ values close to 0.25.

## Metropolis-Hastings Algorithm with Adaptive Random Walk

Using the Metropolis-Hastings Algorithm with adaptive random walk (MHARW), a chain of size $N=10^5$ is generated with a precision of 3 in the proposal distribution, a thinning of 25, and a burn-in of 5000. The graph of the resulting density shows a similar behavior to the one obtained previously.

```{r echo=TRUE, warning=FALSE, results='hide',fig.width=7, fig.height=5}
test=Gen_FC_X1_X2(N=10^5, prop_prec=3, a=a1, b=b1, c=c1, d=d1, v=0.05, option = "all", thin=25, burnin=5000,target_acceptance = 0.4)
plot(density(test$thinned_chain),main="Non-normalized Conditional Distribution Density of X_1 Given X_2",xlab=expression("Values of " ~ X[1]~"given"~X[2]==0.05))
```

## Convergence Monitoring of the Simulation Method

To assess the convergence of the Markov chain generated by the proposed algorithm, key diagnostics are monitored: the **acceptance rate**, **effective sample size (ESS)**, and the **R-hat diagnostic** (Gelman-Rubin statistic). These metrics are evaluated across different values of the **precision parameter** (used in the proposal distribution) and the **conditioning variable** $X_2 = v$

```{r warning=FALSE, echo=TRUE, results='hide'}
df_ess_ar <- results_Mon_Measure(N=10^4, prop_prec_values=seq(1, 20, by = 1), a=a1, b=b1, c=c1, d=d1, v_values=seq(0.01, 0.24, length.out = 10),thin = 5,burnin = 1000,target_acceptance = 0.4)
 df_rhat <- results_Mon_R_Hat(N=10^4, prop_prec_values=seq(1, 20, by = 1), a=a1, b=b1, c=c1, d=d1, v_values=seq(0.01, 0.24, length.out = 10),thin = 5,burnin = 1000,target_acceptance = 0.4)
```

The desired convergence behavior is as follows: - The **acceptance rate** (Figure 3b) should ideally remain between **0.3 and 0.7**. - The **effective sample size** (Figure 3a) should be close to the post burn-in sample size. For the configuration used in this study, the ESS is expected to exceed **465** and approach $(10^4 - 1000) / 5 = 1800$, given the thinning interval of 5 and burn-in of 1000 from a total of 10,000 iterations.

Additionally, the **R-hat diagnostic** (Figure 3c) is computed to evaluate convergence across multiple chains. This statistic compares the variance between chains to the variance within chains. An **R-hat value close to 1** indicates that the chains have converged to the same target distribution, suggesting that the generated samples are representative of the underlying distribution. Conversely, **R-hat values significantly greater than 1** suggest a lack of convergence, and it is recommended to extend the simulation to improve convergence and ensure more reliable estimates.

The panel of convergence plots (Figures 3a–3c) provides a comprehensive view for selecting appropriate values of the **precision parameter** based on the **conditioning variable** $X_2 = v$, ensuring both the efficiency and stability of the sampling process.

```{r fig.width=8, fig.height=10, warning=FALSE, echo=TRUE}
# Example usage:
Generate_Figure3_Panels(df_ess_ar, df_rhat, prop_prec_values=seq(1, 20, by = 1))
```

## Another random sample generated for the conditional distribution of $X_1$ given $X_2$

Another sample of size $N=10^5$ is generated using $\phi = (2.2, 2.2, 2.2, 2.2)$ with a precision of 3, thinning of 25, burn-in of 5000, $X_2 = v = 0.05$, and target acceptance of 0.4. This latter value controls the increase or decrease of the precision during the simulation, meaning the algorithm adjusts itself, which allows for a rapid reduction in the autocorrelation of the chain.

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=8, fig.height=5.5}
ExampleFC_X1_X2=Gen_FC_X1_X2(N=10^5, prop_prec = 3, a=a1, b=b1, c=c1, d=d1, v=0.05, option="all",thin = 25, burnin = 5000, X10_given = "random", target_acceptance = 0.4, dig_tol=15)
Graphs(as.data.frame(ExampleFC_X1_X2$thinned_chain), "X1", width = 40, lscatt = 0.3, uscatt = 0.3)
```

For the results of ExampleFC_X1_X2, the following table presents the acceptance rate before and after the burn-in period, the effective sample size, chain length, and the adjusted precision value. The adjustment period corresponds to the burn-in segment of the chain.

```{r}
library(knitr)
library(kableExtra)

df <- data.frame(
  "Acceptance Rate" = ExampleFC_X1_X2$acc_rate,
  "Acceptance Rate Post Burn-in" = ExampleFC_X1_X2$acc_rate_pos_burnin,
  "ESS" = effectiveSize(ExampleFC_X1_X2$thinned_chain),
  "Length" = length(ExampleFC_X1_X2$thinned_chain),
  "Precision" = ExampleFC_X1_X2$precision,
  row.names = "Chain Measurements"  # Cambia el nombre de la fila
)
df
```

## Convergence Monitoring with Fixed Seeds

The previously simulated samples assumed that the seed was generated randomly. Now, we consider nine user-specified seeds and monitor the convergence of the mean of each generated chain.

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=8.5, fig.height=6}
N=10^5;burnin=5000;thin=25; target_acceptance=0.4
seedgiv=seq(0.1,0.9,0.1)
ExampleFC_X1_X2_seedgiven=matrix(data=NA,nrow = length(seq((burnin+1), N, by = thin)),ncol=9,dimnames=list(list(),list("0.1","0.2","0.3","0.4","0.5","0.6","0.7","0.8","0.9")))
for (i in 1:9) {
  ExampleFC_X1_X2_seedgiven[,i]=Gen_FC_X1_X2(N=N, prop_prec = 3, a=a1, b=b1, c=c1, d=d1, v=0.05, option="all", thin = thin, burnin = burnin, X10_given = seedgiv[i], dig_tol = 10,target_acceptance)$thinned_chain
}
ExampleFC_X1_X2_seedgiven=as.data.frame(ExampleFC_X1_X2_seedgiven)

# Matrix of cumsum of all simulations obtained.
N=nrow(ExampleFC_X1_X2_seedgiven)
ExampleFC_X1_X2_seedgiven_cum=apply(ExampleFC_X1_X2_seedgiven,2,cumsum)/(1:N)
ExampleFC_X1_X2_seedgiven_cum=as.data.frame(ExampleFC_X1_X2_seedgiven_cum)

# Matrix organization for plotting.
ExampleFC_X1_X2_seedgiven_cum=gather(ExampleFC_X1_X2_seedgiven_cum,key="Seed",value="FCmu")
ExampleFC_X1_X2_seedgiven_cum$Sim=rep(1:N,9)
# Function to apply a consistent theme
  custom_theme <- theme_minimal(base_size = 10) +
    theme(
      axis.title = element_text(size = 12),
      axis.text = element_text(size = 9),
      legend.title = element_text(size = 10),
      legend.text = element_text(size = 9),
      plot.margin = margin(10, 10, 10, 10)
    )
# Graphic
Piece1_Grap_FC=ggplot(ExampleFC_X1_X2_seedgiven_cum,aes(x=Sim ,y=FCmu,group= Seed, color=Seed))+geom_line()+ylab(expression("Accumulated Average " ~ hat(X)[1]^(t)))+xlab("Chain Iterations (t)")+xlim(0,50)+custom_theme

Piece2_Grap_FC=ggplot(ExampleFC_X1_X2_seedgiven_cum,aes(x=Sim ,y=FCmu,group= Seed, color=Seed))+geom_line()+ylab(expression("Accumulated Average " ~ hat(X)[1]^(t)))+xlab("Chain Iterations (t)")+xlim(0,250)+custom_theme

Full_Grap_FC=ggplot(ExampleFC_X1_X2_seedgiven_cum,aes(x=Sim ,y=FCmu,group= Seed, color=Seed))+geom_line()+ylab(expression("Accumulated Average " ~ hat(X)[1]^(t)))+xlab("Chain Iterations (t)")+custom_theme

grid.arrange(arrangeGrob(Piece1_Grap_FC, Piece2_Grap_FC, Full_Grap_FC,ncol=2, nrow=2, widths=c(2, 2), heights=c(2,2),layout_matrix=rbind(c(1,2),c(3,3))),bottom="Convergence control using averaging")
```

```{r}
round(apply(ExampleFC_X1_X2_seedgiven[1:3800,], 2, mean),3)
```

# Gibbs Sampling

## Random Samples for the Vector $(X_1, X_2)$

### Convergence Monitoring

The Gibbs Sampling algorithm is used to generate a random sample of the vector $(X_1, X_2)$. For the convergence monitoring of the chains generated for $X_1$ and $X_2$, figures are presented that include density versus histogram, trace, cumulative mean, and autocorrelation.

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=8, fig.height=5.5}
N=10^5
Example_Joint_Dist=Gen_Joint_Dist(N1 = N,N2 = 2,prop_prec = 3,a1,b1,c1,d1,thin = 2,X10_given ="random",target_acceptance = 0.4)
burnin=5000;thin=25
Graphs(as.data.frame(Example_Joint_Dist$X2[seq((burnin+1), N, by=thin)]),"X2",width = 40,uscatt = 0.06,lscatt = 0.05)
```

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=8, fig.height=5.5}
Graphs(as.data.frame(Example_Joint_Dist$X1[seq((burnin+1), N, by=thin)]),"X1",width = 40,uscatt = 0.25,lscatt = 0.2)
```

### Contour Plots and Scatter Plot for the Generated Sample of $(X_1, X_2)$

The scatter plot of the generated sample Example_Joint_Dist is plotted over the contour lines associated with the bivariate distribution $(X_1, X_2)$ with parameters $\phi = (2.2, 2.2, 2.2, 2.2)$.

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=7, fig.height=4}
mu1=seq(0,1,length=10^3)
s1=seq(0,0.25,length=10^3)
dta=expand.grid(X1 = mu1, X2 = s1) %>% 
  mutate(Z = ifelse(X1 * (1 - X1) > X2, X2^(c1 - 1) * (X1 * (1 - X1) - X2)^(d1 - 1) / (X1^(c1 + d1 - a1) * (1 - X1)^(c1 + d1 - b1)), NA))
ggplot()+geom_contour(aes(dta$X1, dta$X2, z = (dta$Z)),bins = 50) + 
  geom_point(aes(x=Example_Joint_Dist$X1[seq((burnin+1), N, by=thin)], y=Example_Joint_Dist$X2[seq((burnin+1), N, by=thin)]), colour="red",size=0.2) + 
  xlab(expression(X[1])) + ylab(expression(X[2])) + 
  labs(title = "Contour Plots and Scatter Plot of a Random Sample")+custom_theme
```

## Random Samples for the Vector $(Y_1, Y_2)$

### Convergence Monitoring

The generated sample Example_Joint_Dist for the vector $(X_1, X_2)$ is now transformed into a sample for the vector $(Y_1, Y_2)$ using the transformation presented at the beginning of this document. For convergence monitoring of the chains for $Y_1$ and $Y_2$, the density and histogram, trace plot, cumulative mean, and autocorrelation are used.

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=8, fig.height=5.5}
piece=(Example_Joint_Dist$X1[seq((burnin+1), N, by=thin)]*(1-Example_Joint_Dist$X1[seq((burnin+1), N, by=thin)])/ (Example_Joint_Dist$X2[seq((burnin+1), N, by=thin)])-1)
alpha=Example_Joint_Dist$X1[seq((burnin+1), N, by=thin)]*piece
beta=(1-Example_Joint_Dist$X1[seq((burnin+1), N, by=thin)])*piece
Graphs(as.data.frame(alpha),"Y1",width = 40,uscatt = 10,lscatt = 10)
```

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=8, fig.height=5.5}
Graphs(as.data.frame(beta),"Y2",width = 40,uscatt = 10,lscatt = 10)
```

### Contour Plots and Scatter Plot for the Generated Sample of $(Y_1, Y_2)$

The scatter plot of the generated sample for the random vector $(Y_1, Y_2)$ is plotted over the contour lines associated with the bivariate distribution $(Y_1, Y_2)$ with parameters $\phi = (2.2, 2.2, 2.2, 2.2)$.

```{r, echo=TRUE, warning=FALSE, results='hide', fig.width=7, fig.height=4}
alp1=seq(0,18,length=10^3)
bet1=seq(0,10,length=10^3)
dta=expand.grid(X1 = alp1, X2 = bet1) %>%
  mutate(Z = X1^(a1-1)*X2^(b1-1)*(X1+X2)^(d1-a1-b1)*(X1+X2+1)^(-c1-d1)/(beta(a1,b1)*beta(c1,d1)))
ggplot()+geom_contour(aes(dta$X1, dta$X2, z = dta$Z),bins = 50)+
  geom_point(aes(x=alpha,y=beta),colour="red",size=0.3)+xlab(expression(Y[1])) + 
  ylab(expression(Y[2])) + 
  labs(title = "Contour Plots and Scatter Plot of a Random Sample")+xlim(c(0,5)) + 
  ylim(c(0,2))+custom_theme
```

# Comparison Between Numerical and Analytical Moments

The function Measure_Diagnostic is used with the sample Example_Joint_Dist to determine the numerical moments, analytical moments, and the difference between them for the vector $(Y_1, Y_2)$. In the implementation of this function, a burn-in of 5000 and a thinning of 25 are used.

```{r, echo=TRUE, warning=FALSE, results='hide'}
results_measure_diag=Measure_Diagnostic(data1 = Example_Joint_Dist$X1,data2 = Example_Joint_Dist$X2, var ="transform", digits = 4, a = a1, b = b1, c = c1, d = d1, burnin = 5000, thin = 25)
```

The numerical results were:

```{r}
results_measure_diag$Numerical
```

The analytical results were:

```{r}
results_measure_diag$Analytical
```

The difference between the numerical and analytical descriptive measures is as follows:

```{r}
results_measure_diag$Differences
```

# Comparison Using a Different Parameter Configuration

```{r, echo=TRUE, warning=FALSE, results='hide'}
a2=3;b2=6;c2=3;d2=6
Example_Joint_Dist1=Gen_Joint_Dist(N1 = 10^5,N2 = 2,prop_prec=4,a = a2,b = b2,c = c2,d = d2,thin = 5, X10_given = "random",target_acceptance = 0.4)

results_measure_diag1=Measure_Diagnostic(data1 = Example_Joint_Dist1$X1,data2 = Example_Joint_Dist1$X2, var ="transform", digits = 4, a = a2, b = b2, c = c2, d = d2, burnin = 5000, thin = 5)
```

The numerical results were:

```{r}
results_measure_diag1$Numerical
```

The analytical results were:

```{r}
results_measure_diag1$Analytical
```

The difference between the numerical and analytical descriptive measures is as follows:

```{r}
results_measure_diag1$Differences
```
